### 2017-07-14 introduction.tex
Minor
Adding related work

% Ability to compute effectively and securely.
To address these concerns, a myriad of computational infrastructures
have been developed. These infrastructures, including our own \NAMENS, 
implement the software required to securely store and analyze protected
data. However, in almost every case, there is one significant weakness in these systems
and that is the humans tasked with administering and managing 
data collections. Most often, the policies and processes for managing
the data are ad hoc and lack software support.

To address these challenges we introduce two abstractions: 
the safe-collection to define the scope of a data collection
and the associated policies and the role of a data steward
to manage safe collections.  These two constructs allow us 
to define, manage, and audit access to, and use of, of 
sensitive data.  We implement these constructs in the

>>>>

% Ability to compute effectively and securely.
To address these concerns, a myriad of computational infrastructures
have been developed. These infrastructures, including our own \NAMENS \cite{babuji2016cloud},
implement the software required to securely store and analyze protected
data. However, in almost every case, there is one significant weakness in these systems
and that is the humans tasked with administering and managing 
data collections. Most often, the policies and processes for managing
the data are ad hoc and lack software support.

To address these challenges we introduce two abstractions: 
the safe-collection to define the scope of a data collection
and the associated policies and the role of a data steward
to manage safe collections.  These two constructs allow us 
to define, manage, and audit access to, and use of, of 
sensitive data.  We implement these constructs in \NAME and
describe how it enhances security.

### 2017-07-14 relatedwork.tex
Adding related work

Secure data enclaves have a long and varied history starting with Air gapped systems that are physically
disconnected from the internet
NORC Data Enclave

>>>>

Secure data enclaves have a long and varied history starting with air gapped systems that are physically
disconnected from the internet.

The NORC \cite{lane2008using} at the University of Chicago offers a FISMA compliant data enclave. The enclave
was designed with the vision of supporting collaboration over a remote access terminals with the microdata hosted
on a NORC server. This approach is fairly common and ensures security by access control, and limiting computation
to the server. This approach is limited by the storage and computational infrastructure backend and is not
suited for large scale data analysis. Furthermore, since a user could read microdata over the terminal, this
system only guarantees the privacy of the bulk of microdata.

The National Center for Health Statistics Research Data Center (RDC) \cite{cdc} hosts a large collection of
restricted datasets. The datasets contain health information and are covered under HIPAA guidelines.
The data is accessible on-premise at NCHS RDC or Federal Statistical RDC, or via remote access although
several datasets are not available for remote access. RDC restricts access to direct identifiers such as name,
social security while leaving indirect identifiers such as geography accessible. Even with the constraints
on access and limited accessibility, access to potentially identifying information leaves this system open to
linkage attacks. This is mitigated to some extent by strong vetting of research proposals.

The NCI Genomic Data Commons \cite{grossman2016toward} at the University of Chicago hosts several Petabytes of
genomic data, and provides an on-premise cloud model to enable computation on these sensitive datasets.
While the on-premise infrastructure meets compliance requirements, this choice leads to added costs in terms of
building an maintaining production compute infrastructure while competing with cloud vendors who has the advantage
of economies of scale and resources to retain talent.
